\cvsection{Experience}

\begin{cventries}
\cventry
    {\textbf{Data Engineer} | Outstanding Performance Evaluation} % Job title
    {Snapcommerce} % Organization
    {Toronto, Canada} % Location
    {May 2021 - Sept 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Fixed and refactored highly critical failing \descriptionstylebold{Airflow} pipeline getting data from Google Ads \descriptionstylebold{gRPC APIs}, decreasing run-time by \descriptionstylebold{100\%}.}
        \item {Built Product Catalogue infrastructure, sourcing and transforming raw feeds from Shopify product APIs to Snowflake dim \& fact tables, finally product listing platforms. \descriptionstylebold{Saving ~20 hours/week} of manual work. Built using \descriptionstylebold{Python, Airlfow, dbt, SQL and AWS S3}}
        \item {Designed and Built \descriptionstylebold{Airlow} pipelines to get 10,000+ daily updates to product inventory data from \descriptionstylebold{REST APIs} into \descriptionstylebold{AWS S3 buckets}.}
        \item {Built  \descriptionstylebold{14 downstream dbt models} to model raw source data into fact and dimension tables}
        %\item {Proposed and built JIRA and PR templates improving ticket and code quality, and enforcing standards on data quality as team grows.}
      \end{cvitems}
    }
  \cventry
    {\textbf{Data Scientist} | Outstanding Performance Evaluation} % Job title
    {Intact Financial - Data Lab} % Organization
    {Toronto, Canada} % Location
    {Sept 2020 - Dec 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {\descriptionstyleboldcolor{Project:} Predict the loss cost of a policy holder using \descriptionstylebold{XGBoost Regressor model} optimised on \descriptionstylebold{TweedieLogLoss metric}.}
        \item {Improved ML model evaluation memory efficiency, and run-time by \descriptionstylebold{30\%}, by implementing cached feature matrices, \descriptionstylebold{saving ~7 hours} of compute per week.}
        \item {Rebuilt internal data visualization packages, resulting in \descriptionstylebold{300x} improvement in run-time, and saving \descriptionstylebold{12 hours/week} for \descriptionstylebold{8+} teams.}
        \item {Developed a new Model Evaluation Pipeline using \descriptionstylebold{Bash and Python} to save \descriptionstylebold{1.5 weeks} of run-time and \descriptionstylebold{3 days of developer time} per month.}
      \end{cvitems}
    }

  \cventry
    {\textbf{Data Scientist} | Outstanding Performance Evaluation} % Organization
    {TD Bank} % Job title
    {Toronto, Canada} % Location
    {Jan. 2020 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {\descriptionstyleboldcolor{Project}: Predict the best premium credit card for TD Bank customers using \descriptionstylebold{XGBoost Classifier} optimised on \descriptionstylebold{LogLoss metric} generating \descriptionstylebold{$\$$1MM CAD} anually.}
        %\item {Independently built the \descriptionstylebold{Multi-Class Classification} Model Using \descriptionstylebold{XGBoost}, \descriptionstylebold{HyperOpt} for \descriptionstylebold{Hyper Parameter Tuning} and, \descriptionstylebold{SHAP} for feature importance, all done in \descriptionstylebold{Python}.}
        \item {Built End to End product to predict the best premium credit card for customers using \descriptionstylebold{Multi-Class Classification} model optimised on \descriptionstylebold{LogLoss metric} using \descriptionstylebold{Python}, \descriptionstylebold{XGBoost}, Hyperopt, SHAP and Bash generating \descriptionstylebold{$\$$1MM CAD} annually.}
        \item {Rebuilt the \descriptionstylebold{ETL with Feature Engineering pipelines }, decreasing the run-time by \descriptionstylebold{200x} while making the code base more modular and accessible to future developers.}
        \item {Developed new Employee Credit Card products generating \descriptionstylebold{\$9 MM CAD} in Annual Profit and \descriptionstylebold{35\%} increase in user acquisition.}
      \end{cvitems}
    }

  \cventry
    {\textbf{Data Scientist} | Outstanding Performance Evaluation} % Job title
    {Scotiabank - Data Science Lab} % Organization
    {Toronto, Canada} % Location
    {Sept. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {\descriptionstyleboldcolor{Project}: \descriptionstylebold{Build and lead} a Product \descriptionstylebold{Recommendation Engine} to assist Scotiabank Sales team using \descriptionstylebold{Django} and \descriptionstylebold{XGBoost models}.}
        \item {Developed pipeline to clean and analyse 20+ thousand sentences of user feedback data using \descriptionstylebold{LDA model (NLP)}, \descriptionstylebold{saving 1+ month of manual work}.}
        %\item Revamped the user feedback system improving the user engagement score by \descriptionstylebold{50\%}!
        \item {Proposed and built Justification Engine to provide reasoning behind recommendations to the sales team, using \descriptionstylebold{XGBoost, SHAP, Django, SQL, JavaScript and AJAX}.}
        %\item {Proposed and built a new feature to help Scotiabank support Women Led Businesses and promote equal opportunity, using \descriptionstylebold{Django, SQL, JavaScript \& AJAX}.}
        \item {\descriptionstylebold{Lead} a team of Engineers and Data Scientists, and shipped the recommendation engine \descriptionstylebold{1 month} ahead of schedule!}
      \end{cvitems}
    }

  \cventry
    {\textbf{Research Analyst / Full Stack Developer} | Outstanding Performance Evaluation} % Job title
    {Pattern Analysis and Machine Intelligence Lab at UWaterloo} % Organization
    {Waterloo, Canada} % Location
    {Jan. 2019 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and launched a \descriptionstylebold{Dockerized Flask Web App} to help large (20+ researchers) research teams easily access, manage and analyse datasets stored on \descriptionstylebold{Azure PSQL Database}, saving the research group \descriptionstylebold{\$8k CAD annually}!}
		\item {Built an \descriptionstylebold{ARIMA time series model} to forecast procurement prices of fresh produce using \descriptionstylebold{Python and MATLAB}.}
        \item {\descriptionstylebold{Managed} an engineer to help push the app in production.}
      \end{cvitems}
    }
\end{cventries}
